Persistence of marine populations under climate and fishing

### 2014-07-11 Writing/Appendix.tex
adding a bit about MPAs in methods/results

\subsection{Re-allocation of Effort \label{effort}}
~\\Spatial shifts of harvesters in response to MPA creation can affect sustainability of the system. We model the two extremes of response: either that harvesting pressure that occurred in now-MPAs is reallocated outside the reservers, or harvesting inside MPAs disappears from the system with the creation of MPAs and MPAs are effectively an effort control management technique. To reallocate effort we increased quota by 50\% in outside of MPAs.

>>>>

\subsection{Re-allocation of Effort \label{effort}}
~\\Spatial shifts of harvesters in response to MPA creation can affect sustainability of the system \citep{Botsfordetal2009}. We model the two extremes of response: either that harvesting pressure that occurred in now-MPAs is reallocated outside the reservers, or harvesting inside MPAs disappears from the system with the creation of MPAs and MPAs are effectively an effort control management technique. To reallocate effort we increased quota by 50\% in outside of MPAs (see \cite{Kaplanetal2005} for similar approach).
